CGAT In The Hat

### 2012-12-06 paper/paper.tex
Fixed latex error

\paragraph{GET Requests}
\begin{itemize}
\item administration_info - Provides the user with meta information information that the user would need to perform administrative tasks such as creating a group or assigning a task.
\item annotation - Provide the user with information about an specified annotation.
\item contig - Get information about a specific contig.
\item gene - Get information about a specific gene.
\item group - Get information about a specific group.
\item help - Get help information on a specific topic.
\item user_profile - Get the profile information about a specific user. If the user is logged in and requests information about themselves, more information is provided.
\end{itemize}

@@

\begin{itemize}
\item assign_task - Ask a group of people to perform an annotation.
\item cancel_notification - Clear a notification from a user.
\item create_annotation - Create a new annotation of a contig.
\item create_group - Create a group.
\item join_group - Join a group.
\item leave_group - Leave a group.
\item login - Login.
\item logout - Logout.
\item parse_fasta - Upload a FASTA file to the server, parse the contents, and returned the parsed structure.
\item register - Register a new user.
\item save_annotation - Save a work-in-progress annotation.
\item set_help - Upload a help page.
\item submit_annotation - Submit a finalized annotation.
\item upload_contig - Upload a contig into CGAT.
\end{itemize}

>>>>

\paragraph{GET Requests}
\begin{itemize}
\item administration\_info - Provides the user with meta information information that the user would need to perform administrative tasks such as creating a group or assigning a task.
\item annotation - Provide the user with information about an specified annotation.
\item contig - Get information about a specific contig.
\item gene - Get information about a specific gene.
\item group - Get information about a specific group.
\item help - Get help information on a specific topic.
\item user\_profile - Get the profile information about a specific user. If the user is logged in and requests information about themselves, more information is provided.
\end{itemize}

@@

\begin{itemize}
\item assign\_task - Ask a group of people to perform an annotation.
\item cancel\_notification - Clear a notification from a user.
\item create\_annotation - Create a new annotation of a contig.
\item create\_group - Create a group.
\item join\_group - Join a group.
\item leave\_group - Leave a group.
\item login - Login.
\item logout - Logout.
\item parse\_fasta - Upload a FASTA file to the server, parse the contents, and returned the parsed structure.
\item register - Register a new user.
\item save\_annotation - Save a work-in-progress annotation.
\item set\_help - Upload a help page.
\item submit\_annotation - Submit a finalized annotation.
\item upload\_contig - Upload a contig into CGAT.
\end{itemize}
